Procurements of the Canadian Government, Runaway Military Contracts

### 2024-11-30 paper/paper.qmd
added small and big contracts graph

df_table <- df %>% select(-contract, -start_date, -end_date)

@@

>>>>

df_table <- df %>% select(-contract, -start_date, -end_date, -link)

@@

```{r fig-small-big}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

# Step 1: Create a new column 'contract_size' categorizing contracts
df <- df %>%
  mutate(
    contract_size = ifelse(amount <= 100000, "Small Contracts (≤ 100k)", "Big Contracts (> 100k)")
  )

# Summarize total amount spent per contract size category
total_spent_df <- df %>%
  group_by(contract_size) %>%
  summarize(
    total_amount_spent = sum(amount, na.rm = TRUE)
  ) %>%
  ungroup()

# Convert the total amount to billions of CAD
total_spent_df <- total_spent_df %>%
  mutate(total_amount_billion = total_amount_spent / 1e9)

# Optional: Display the summarized data
print(total_spent_df)

# Create the bar chart
ggplot(total_spent_df, aes(x = contract_size, y = total_amount_billion, fill = contract_size)) +
  geom_bar(stat = "identity", width = 0.6) +
  geom_text(aes(label = paste0(round(total_amount_billion, 2), "B")), 
            vjust = -0.5, 
            size = 5) +  # Adds labels above the bars
  scale_fill_manual(
    values = c("Small Contracts (≤ 100k)" = "steelblue", "Big Contracts (> 100k)" = "tomato")
  ) +
  scale_y_continuous(
    labels = scales::number_format(scale = 1, suffix = "B"),  # Displays y-axis in billions
    expand = expansion(mult = c(0, 0.1))  # Adds space above the bars for labels
  ) +
  labs(
    title = "Total Amount Spent on Contracts",
    subtitle = "Comparison between Small (≤ 100k CAD) and Big (> 100k CAD) Contracts",
    x = "Contract Size",
    y = "Total Amount Spent (Billions of CAD)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 14),
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 16),
    legend.position = "none",  # Removes the legend as it's redundant
    plot.caption = element_text(hjust = 0.5, size = 10, face = "italic")
  )
